---
title: "Formative Assessment 7"
author: "DESQUITADO, Yuichi P."
date: "2023-04-19"
output: html_document
---

Link for GitHub: []()

# Exercise 15.1 

1. A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

(a) Calculate the probability that a memory stick will be scrapped.
(b) Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance.

```{r}



```

2. Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf

$$f(x) = 0.025x + b, 2 < x <6$$

(a) Show that, for this to be a genuine probability density, $b = 0.15$.
(b) Find the probability that the measurement of the current exceeds 3 A.
(c) Find $E(X)$.

```{r}



```

3. In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in $[-\pi, \pi]$. Find $P(X \le 0)$ and $P(X \le \pi/2)$.