---
title: "Formative Assessment 7"
author: "DESQUITADO, Yuichi P."
date: "2023-04-19"
output: html_document
---

***Link for GitHub: [https://github.com/ydesquitado/APM1110_FA7.R](https://github.com/ydesquitado/APM1110_FA7.R)***

# Exercise 15.1 

## 1. A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

(a) Calculate the probability that a memory stick will be scrapped.
(b) Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance.

### For Letter A

```{r}

minLength <- 2 #Shortest possible length
maxLength <- 12 #Longest possible length
totalLength <- 12 - 2 #Total length accounted for the problem
scrappedLength <- 12 - 10 #Portion of length that will be scrapped
scrappedProb <- scrappedLength/totalLength #Probability of a it being scrapped
scrappedProb #Answer for letter A

```

### For Letter B

```{r}

runs <- 50 #Number of simulations
sims <- runif(50, 2, 12) #Simulation of production of 50 sticks ranging from 2mm to 12mm
hist(sims,
     breaks = 10,
     xlab = "Length of Sticks",
     ylab = "Frequency of lengths",
     col = "light pink")
simsMean <- mean(sims) #Average of the sims
simsMean
simsVar <- var(sims) #Variance of the sims
simsVar

```

---

## 2. Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf

$$f(x) = 0.025x + b, 2 < x <6$$

(a) Show that, for this to be a genuine probability density, $b = 0.15$.
(b) Find the probability that the measurement of the current exceeds 3 A.
(c) Find $E(X)$.


### For Letter A

To first determine the genuineness of the probability density, we have to show the following:

* The area under the curve is $1$. *(This is done by getting the integral of the function from* $[-\infty, \infty]$*.)*

* The function $f(x)$ is non-negative *(It is greater than or equal to *$0$*.)*

```{r}

b <- 0.15 #Value of b that is given

curve ((0.025 * x) + b, 
       2, 
       6, 
       xlim = c(0, 8),
       xlab = "x",
       ylab = "0.025x + b")

```

Since $f(x)$ is bounded $[2, 6]$, we will integrate said function from $2$ to $6$.

```{r}

integrand <- function(x)(0.025 * x + 0.15)

integrate(integrand, 2, 6) #The bounds in question span from 2 to 6

```

The "with absolute error < 1.1e-14" only means that the error of computation is less than $1.1 \times 10^{-14}$, which is entirely insignificant since R has computed the integral numerically (Horgan, p. 330).

Thus, the $\int_2^6{0.025x + 0.15dx}=1$, which satisfies the first point.

For the second point, the plot has shown that the curve is illustrated above x-axis in any points within the bounds $[2,6]$, thus $f(x)$ is non-negative (or greater than or equal to 0)

### For Letter B

```{r}

integrate(integrand, 3, 6) #The bound asked spans from 3 to 6

```

$$
P(3 < X < 6) = \int_3^6{0.025x+0.15}dx \\ = \left[ \frac{0.025x^2}{2}  + 0.15x \right]_3^6  \\ = \left( \frac{0.025(6)^2}{2} + 0.15(6) \right) - \left( \frac{0.025(3)^2}{2} + 0.15(3) \right) \\ = \frac{27}{20} - \frac{9}{16} \\ = \frac{63}{80} = 0.7875
$$
### For Letter C

To get $E(X)$, we have to get the product of $x$ and $f(x)$ first then integrate them.

```{r}

expectedIntegrand <- function(x)(x * (0.025 * x + 0.15))

integrate(expectedIntegrand, 2, 6)

```

---

### 3. In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in $[-\pi, \pi]$. Find $P(X \le 0)$ and $P(X \le \pi/2)$.

According to definition 15.3 from "Probability with R: An Introduction with Computer Science Application" (2020), the probability density function of a continuous uniform distribution is:

$$
f(x) = \cases { \frac{1}{b - a}, & $a \le x \le b$ \cr 0, & $otherwise$ }
$$

*Note: There is no need to get the integral of pdf as the plot of* $\frac{1}{b - a}$ *is 1, given that the base is equal to* $b - a$ *while the height is* $\frac{1}{b - a}$ *, which gives us* 

$$
A_{pdf} = BH = (b - a) \times \frac{1}{b - a} = 1
$$ *(Horgan, p. 332).*

With this definition, the pdf of the said problem is:

$$
f(x) = \frac{1}{\pi - (-\pi)} \\ = \frac{1}{\pi + \pi} \\ = \frac{1}{2\pi}
$$
and

$$
A_{pdf} = (\pi - (-\pi) \times \frac{1}{\pi - (-\pi)}) \\ = ((\pi + \pi) \times \frac{1}{\pi + \pi}) \\ = 2\pi \times \frac{1}{2\pi}
$$

To get the $P(X \le 0)$, we use the bounds $[-\pi, 0]$ and using `punif()`.

```{r}

punif(0, -pi, pi)

```

$$
P(X \le 0) = \int_{-\pi}^0{\frac{1}{2\pi}}dx \\ = \left[ \frac{x}{2\pi} \right]_{-\pi}^0 \\ = 0 - (\frac{-\pi}{2\pi}) \\ = 0 + \frac{1}{2} \\ = \frac{1}{2}
$$

Same as the previous problem, we can get the $P(X \le \pi/2)$.

```{r}

punif(pi / 2, -pi, pi)

```

$$
P(X \le \pi/2) = \int_{-\pi}^{\frac{\pi}{2}}{\frac{1}{2\pi}}dx \\ = \left[ \frac{x}{2\pi} \right]_{-\pi}^{\frac{\pi}{2}} \\ = \frac{\frac{\pi}{2}}{2\pi} - (-\frac{\pi}{2\pi}) \\ = (\frac{\pi}{2} \times \frac{1}{2\pi}) + \frac{1}{2} \\ = \frac{1}{4} + \frac{1}{2} \\ = \frac{1}{4} + \frac{2}{4} \\ = \frac{3}{4} \\ = 0.75
$$